Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-03-14 paper/supplemental_information.Rmd
supplement

---
title: "Supplemental Information"
output: pdf_document
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(here)
source(here("helper","common.R"))
```

```{r, echo=FALSE}
knitr::purl(here("paper","paper.Rmd"), documentation = 0)
suppressMessages(source(here("paper.R")))
```

@@

```{r, fig.env="figure*"}
ggplot(d_sub, aes(x = age))+ 
  geom_histogram(binwidth = 1) + 
  facet_wrap(~dataset_name, scale = "free_y")
```

```{r, fig.cap="Number of administrations for datasets with repeated measurements."}

@@

```{r, results = "asis"}

@@

```{r results="asis"}
papaja::apa_table(acc_mods_lmer_summary)
```

```{r results="asis"}
papaja::apa_table(rt_mods_lmer_summary)
```

With our current dataset we cannot specifically determine whether within-individual patterns of change conform to power law or exponential forms [@kail1991,@heathcote2000], but regardless we see clear patterns of developmental change related to skill acquisition.

@@

fit3_long <- sem(fa3_model_long, d_sub_wide, std.lv=TRUE, missing='fiml')

@@

```{r}
layout <- read.csv(here("misc/layout_dt3.csv"), header = FALSE)

graph_sem(model = fit3_long, text_size = 3, layout=t(layout))

>>>>

---
title: "Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood"
output: pdf_document
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library(here)
source(here("helper","common.R"))
```

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
knitr::purl(here("paper","paper.Rmd"), documentation = 0)
suppressMessages(source(here("paper.R")))
```

@@

Figure \ref{fig:dataset} gives the age distribution for each paper within our full dataset.

```{r dataset, fig.env="figure*"}
ggplot(d_sub, aes(x = age))+ 
  geom_histogram(binwidth = 1) + 
  facet_wrap(~dataset_name, scale = "free_y")
```

Figure \ref{fig:longitudinal_admins} shows the distribution of measurement intervals for longitudinal studies within the dataset.

```{r longitudinal_admins, fig.cap="Number of administrations for datasets with repeated measurements."}

@@

Table \ref{tab:corrs} shows pairwise correlations between the primary variables of interest in the dataset.

```{r corrs, results = "asis"}

@@

Table \ref{tab:accmods} shows model comparison measures between for different models of the functional form for accuracy and Table \ref{tab:rtmods} shows the same for reaction time. Note that all of these comparisons With our current dataset we cannot specifically determine whether within-individual patterns of change conform to linear, power law, or exponential developmental patterns [@heathcote2000].

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\begin{tabular}{lllllllll}
\toprule
n. obs & \multicolumn{1}{c}{sigma} & \multicolumn{1}{c}{logLik} & \multicolumn{1}{c}{AIC} & \multicolumn{1}{c}{BIC} & \multicolumn{1}{c}{REMLcrit} & \multicolumn{1}{c}{df.residual} & \multicolumn{1}{c}{model} & \multicolumn{1}{c}{r2}\\
\midrule
48354 & 0.28 & -8,338.83 & 16,691.65 & 16,753.16 & 16,677.65 & 48347 & lwa\_lin & 0.14\\
48354 & 0.28 & -8,305.39 & 16,624.78 & 16,686.28 & 16,610.78 & 48347 & lwa\_log & 0.12\\
50244 & 0.31 & -12,486.60 & 24,987.21 & 25,048.98 & 24,973.21 & 50237 & swa\_lin & 0.09\\
50244 & 0.31 & -12,458.77 & 24,931.54 & 24,993.31 & 24,917.54 & 50237 & swa\_log & 0.08\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\begin{tabular}{lllllllll}
\toprule
n. obs & \multicolumn{1}{c}{sigma} & \multicolumn{1}{c}{logLik} & \multicolumn{1}{c}{AIC} & \multicolumn{1}{c}{BIC} & \multicolumn{1}{c}{REMLcrit} & \multicolumn{1}{c}{df.residual} & \multicolumn{1}{c}{model} & \multicolumn{1}{c}{r2}\\
\midrule
18940 & 0.45 & -12,414.69 & 24,843.38 & 24,898.32 & 24,829.38 & 18933 & log\_lin & 0.21\\
18940 & 0.45 & -12,393.27 & 24,800.53 & 24,855.48 & 24,786.53 & 18933 & log\_log & 0.21\\
18940 & 570.49 & -147,644.43 & 295,302.87 & 295,357.81 & 295,288.87 & 18933 & lin\_lin & 0.18\\
18940 & 570.02 & -147,622.67 & 295,259.34 & 295,314.29 & 295,245.34 & 18933 & lin\_log & 0.18\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

```{r accmods, results="asis", include = FALSE}
papaja::apa_table(acc_mods_lmer_summary)
```

```{r results="asis", include = FALSE}
papaja::apa_table(rt_mods_lmer_summary)
```

@@

fit3_long <- sem(fa3_model_long, d_sub_wide_fine, std.lv=TRUE, missing='fiml')

@@

```{r}
layout <- read.csv(here("misc/layout_dt3.csv"), header = FALSE)
graph_sem(model = fit3_long, text_size = 3, layout=t(layout))
